Reproducible and programmatic generation of neuroimaging visualisations

### 2022-04-04 manuscript.Rmd
rep para remove

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
date: "09/03/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

@@

Neuroimaging data are often spatially 3D and can have multiple time
points, adding a 4th dimension (e.g. fMRI data). Thus, communicating
findings or evaluating quality using static 2D slices is challenging.
While well curated 3D renderings can help with spatial localisation
(cite madan), in the end, static 2D images can only provide an
incomplete representation of 3D or 4D data. A added advantage of some of
code-based tools is that you can generate 'rich' media like interactive
figures or animations, which can improve scientific communication of
findings. Many code-based software tools now allow for the generation of
animated brain visualisations (cite blog) or interactive widgets which
allow users to zoom, rotate and scroll through slices. Linking to or
even embedding these videos or interactive figures in papers can greatly
enhance the communication of findings.

>>>>

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
date: "09/03/2022"
output:
  word_document: default
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

@@
